Probing internal structure of distant quasars using Microlensing

### 2014-04-15 paper1/theory.tex
simple captions added

@@

\begin{figure}
\includegraphics[width = .8\textwidth]{plots/lightcurve_gaussian_1.eps}
\caption{\label{fig:lightcurve_gauss} Lightcurve 1.}
\end{figure}

@@

\begin{figure}
\includegraphics[width = .8\textwidth]{plots/lightcurve_disc_1.eps}
\caption{\label{fig:lightcurve_disk} Lightcurve 2.}
\end{figure}

@@

\begin{figure}
\includegraphics[width = .8\textwidth]{plots/lightcurve_crescent_1.eps}
\caption{\label{fig:lightcurve_crescent} Lightcurve 3.}
\end{figure}

@@

>>>>

\begin{figure}
\includegraphics[width = .8\textwidth]{plots/figure_rhalf.eps}
\caption{\label{fig:lightcurve_crescent} Geometry of crescent sources.}
\end{figure}

@@

\begin{figure}
\includegraphics[width = .8\textwidth]{plots/4source_magnification.eps}
\caption{\label{fig:lightcurve_gauss} Lightcurves of crescents, gaussian and disk for sources with identical $S_0$ and $r_{1/2}$. Crescent source has $r_{1/2}$ = 0.72754 $R_p$, $R_n$ = 0.4 $R_p$, a = 0.3/-0.3 $R_p$ }
\end{figure}

@@

\begin{figure}
\includegraphics[width = .8\textwidth]{plots/4avar_magnification.eps}
\caption{\label{fig:lightcurve_disk} Lightcurves of crescent sources with $R_n$ = 0.4 $R_p$.}
\end{figure}

@@

\begin{figure}
\includegraphics[width = .8\textwidth]{plots/4rn_magnification.eps}
\caption{\label{fig:lightcurve_crescent} Lightcurves of backwards crescents with  a = 0.3 $R_p$.}
\end{figure}

@@

\begin{figure}
\includegraphics[width = .8\textwidth]{plots/4rn2_magnification.eps}
\caption{\label{fig:lightcurve_crescent} Lightcurve of forwards crescents with a = -0.3 $R_p$.}
\end{figure}
